### 2010-02-24 trunk/deliverables/D2_2_Ontology/fast_d2_2_2_ontology.tex
extended text for templating section
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@598 d8b0c59b-6544-0410-94d9-83a5658a058e

Figure \ref{fig:templating_example_graph} illustrates the same example graphically, using different colours to represent the two different graphs: the red graph in the background represents the original template resource, whereas the green graph in the front in represents the resource copy as it would be used in a concrete screen flow.

>>>>

Figure \ref{fig:templating_example_graph} illustrates the same example graphically, using different colours to represent the two different graphs: the red graph $G_1$ in the background represents the original template resource, whereas the green graph $G_2$ in the front in represents the resource copy as it would be used in a concrete screen flow. \texttt{catalogue:LoginScreen} $\subset I_{template}$ has been changed to \texttt{catalogue:LoginScreen\_74382} $\subset I_{copy}$.
